### 2014-07-21 Docs/mg/mg.tex
flowchart for the cell-centered MG

\item {\tt dd}: The residual/defect, $ff - L\phi$

@@

>>>>

\item {\tt dd}: The residual/defect, $f - L\phi$

@@

\section{Flowchart}

\MyArrow[1em]{start1}{end1}{colorii,line width=2pt}
\MyArrow[1em]{start2}{end2}{colorii,line width=2pt}

\subsection{Cell-Centered MG}

\item {\tt stencil\_fill\_cc\_all\_mglevels} / {\tt stencil\_fill\_cc}:

\item {\tt ml\_cc}:

\item {\tt mg\_tower\_v\_cycle} (recursive):
\begin{itemize}

  \item {\em recursively descend V-cycle}
  \begin{itemize} 
  \item \tikzmark{end1} {\tt cc\_mg\_tower\_smoother}:

  \item {\tt compute\_defect}:

  \item\tikzmark{start1} {\tt ml\_restriction}:
  \end{itemize}

  \item {\tt mg\_tower\_bottom\_solve}:

  \item {\em ascend V-cycle}

  \begin{itemize}
  \item\tikzmark{end2} {\tt mg\_tower\_prolongation}: Take the solution at level $n-1$ and use it to 
     correct the solution at level $n$ by representing the data on the finer grid.  This uses
     linear reconstruction for jumps by $2\times$ and piecewise-constant otherwise.

  \item\tikzmark{start2} {\tt cc\_mg\_tower\_smoother}:
  \end{itemize}

\end{itemize}
\item multiple {\tt compute\_defect} calls:
